Describing demographic models is hard

### 2020-05-19 paper.tex
ghost clarification

To illustrate the demography API, \msprime\ included a description of a widely-used
three population Out-of-Africa model~\citep{gutenkunst2009inferring} 
as part of its tutorial documentation. In this model (Fig.~\ref{fig:ooa_stats}A),
Eurasian (CEU and CHB) and African (YRI) populations split from each other in the deep past,
followed by a more recent split of European and Asian populations, with variable rates of
continuous migration between each of the populations. However, the implementation in the
\msprime\ tutorial was incorrect. Namely, at the time of the split between African and Eurasian
populations, migration between those two populations was allowed to continue for all time into the
past. Even though the population split was implemented correcly, the specified demographic model had 
an additional ghost population prior to the earliest split (Fig.~\ref{fig:ooa_stats}B).

Fortunately, the effect of this error is subtle. Population sizes and structure since the time of
the split are unaffected, so that differences in expected $F_{ST}$ are negligible between
the correct and incorrect model. However, the presence of a ghost population
changes the distribution of $T_{MRCA}$ in the deep past
is distorted and increases expected heterozygosity in each of the three
populations by up to $4\%$ (Fig.~\ref{fig:ooa_stats}C-G).

>>>>

To illustrate the demography API, \msprime\ included a description of a widely-used
three population Out-of-Africa model~\citep{gutenkunst2009inferring} 
as part of its tutorial documentation. In this model (Fig.~\ref{fig:ooa_stats}A),
Eurasian (CEU and CHB) and African (YRI) populations split from each other in the deep past,
followed by a more recent split of European and Asian populations, with variable rates of
continuous migration between each of the populations. However, the implementation in the
\msprime\ tutorial was incorrect. Namely, at the time of the split between African and Eurasian
populations, migration between those two populations was allowed to continue for all time into the
past. Even though the population split was implemented correctly, the specified demographic model had 
an additional population prior to the earliest split exchanging migrants with the ancestral population 
(Fig.~\ref{fig:ooa_stats}B) but not contributing otherwise to present-day populations.

Fortunately, the effect of this additional 'ghost' population are subtle. Population sizes and structure since the time of
the split are unaffected, so that differences in expected $F_{ST}$ are negligible between
the correct and incorrect model. However, the presence of the ghost population increases
the effective population size and thus affects the distribution of older $T_{MRCA}$ and the expected 
heterozygosity in each of the three populations by up to $4\%$ (Fig.~\ref{fig:ooa_stats}C-G).
